### 2020-09-01 paper/main.tex
Implementation WIP

\chapter{Perfect Graphs}
\input{perfectGraphs.tex}

\chapter{Recognizing Berge Graphs}

\section{Implementation}

Anything interesting about algo/data structure?\\

\subsection{Optimizations}\label{Optimizations}
Bottlenecks in performance (next path, are vectors distinct etc).\\
\TODO{In our graph preprocessing we have a pointer to next edge in order to speed up generating next path.}
\TODO{We used callgrind to get idea of methods crucial for time.}
\TODO{In general enumerating all paths is crucial. As is checking if vector has distinct values.}
\TODO{Jewels -- we iterate all possibly chordal paths and check if they are ok - much faster}
\TODO{$\T_1$ -- we iterate all paths of length 4 and check if there exists a fifth vertex to complete the hole - much faster than iterating vertices.}

Validity tests - unit tests, tests of bigger parts, testing vs known answer and vs naive.

\section{Parallelism with CUDA (?)}

TODO

\section{Experiments}

Naive algorithm - brief description, bottlenecks optimizations (makes huge difference).\\

Description of tests used.\\

Results and Corollary - almost usable algorithm.

\chapter{Coloring Berge Graphs}

\section{Ellipsoid method}

Description.\\

Implementation.\\

Experiments and results.\\

\section{Combinatorial Method}

Cite the paper.\\

On its complexity - point to appendix for pseudo-code.

>>>>

\chapter{Perfect Graphs}
\input{perfectGraphs.tex}
\input{coloringBergeGraphs.tex}

\chapter{Implementation}
\input{implementation.tex}
